---
title: "GuavaFluoresence_TwoIND"
author: "Edwin Eliasson"
date: "9/6/2021"
output: html_document
---
---
title: "GuavaFluorecense"
author: "Edwin Eliasson (From Angelo Limeta)"
date: '2021-09-02'
output: html_document
---


## Load libraries
```{r, echo=FALSE}
library(flowCore)
library(tidyverse)
library(viridis)
library(hrbrthemes)
library(hexbin)
library(data.table)
library(ggpubr)

filter = dplyr::filter
select = dplyr::select
```

## Load data

All data is in csv format in the "../data/2021-08-27_at_08-43-55am" folder
```{r,warning=FALSE}
filenames = list.files(path = "../data/2021-09-01_at_07-42-02am/",full.names = T)

# Extract plate position from filename
plate_pos = filenames %>% gsub(".CSV","",.) %>% gsub(".*am.","",.)

# Loop through and merge all files into a big tibble
tbl = tibble()
for (i in 1:length(filenames)) {
  tbl_file = fread(filenames[i]) %>% mutate(POS = plate_pos[i])
  tbl = rbind(tbl,tbl_file)
}
rm(tbl_file)
```

## Pre-procesing

Replacement of hypgen (-) in columns
```{r}
names(tbl) <- gsub("\\-",".", names(tbl))
glimpse(tbl)
```

## Filter out cells with negative intensity and log transform
```{r}
tbl =
  tbl %>% 
  filter(GRN.B.HLog > 0) %>%
  filter(RED.R.HLog > 0) %>%
  filter(FSC.HLin > 500) 

```


Convert into tidy tibble and add channel info
```{r}
tbl_tidy =
  tbl %>% 
  pivot_longer(-c(POS,TIME),names_to = "CHANNEL",values_to = "INTENSITY") %>% 
  mutate(SCALE = ifelse(grepl("Lin",CHANNEL),"lin","log")) %>% 
  filter(CHANNEL != "RED.R.W")

glimpse(tbl_tidy)
```

Format meta data
```{r}
tbl_meta = 
  fread(file = "../data/plate_map2.csv") %>% 
  mutate(DOSE = as.character(DOSE)) %>% 
  mutate(DOSE_1 = as.character(DOSE_1)) %>% 
  mutate(DOSE_2 = as.character(DOSE_2))
```

Merge meta data with flow cytometry data
```{r}
tbl_tidy =
  tbl_tidy %>% 
  full_join(tbl_meta,by = "POS")

head(tbl_tidy)
```

Matrix with flipped columnes
```{r}
tbl_red_green =

tbl_tidy %>% 
  filter(CHANNEL %in% c("FSC.HLog","GRN.B.HLog", "RED.R.HLog")) %>% 
  pivot_wider(names_from = CHANNEL,values_from = INTENSITY)
  
glimpse(tbl_red_green)
```


#head(tbl_tidy)

Plot Cup1 (log-scale)
```{r,fig.width=8,fig.height=5}

tbl_tidy %>% 
  filter(SCALE == "log") %>% 
  filter(STRAIN %in% c("CUP","CENPK")) %>% 
  filter(NUM.IND %in% c("1")) %>% 
  filter(CHANNEL %in% c("RED.R.HLog")) %>% 
  filter(INDUCER_1 %in% c("Cup","None")) %>% 
  #mutate(DOSE = ifelse(INDUCER == "None",""))
  mutate(DOSE_1 = factor(DOSE_1,levels = c("0","100","500","1000"),ordered = TRUE)) %>%
  ggplot(aes(x = DOSE_1,y = INTENSITY,group = DOSE_1,fill = DOSE_1)) +
  geom_violin(color = "black",draw_quantiles = 0.5) +
  facet_wrap(vars(CASE_CTRL),ncol = 10) +
  xlab("Copper (uM)") +
  ylab("Intesity (a.u.)") +
  theme_bw() +
  stat_compare_means(ref.group = "0",label = "p.signif")
  #scale_fill_manual(values = c("green3","red3")) +
  #scale_color_manual(values = c("green4","red4")) +
```

Plot Estradiol (log-scale)
```{r,fig.width=8,fig.height=5}

tbl_tidy %>% 
  filter(SCALE == "log") %>% 
  filter(STRAIN %in% c("Estradiol","CENPK")) %>% 
  filter(NUM.IND %in% c("1")) %>% 
  filter(CHANNEL %in% c("GRN.B.HLog")) %>% 
  filter(INDUCER_1 %in% c("Estradiol","None")) %>% 
  #mutate(DOSE = ifelse(INDUCER == "None",""))
  mutate(DOSE_1 = factor(DOSE_1,levels = c("0","1e-05","1e-04","0.001","0.01"),ordered = TRUE)) %>%
  ggplot(aes(x = DOSE_1,y = INTENSITY,group = DOSE_1, fill = DOSE_1)) +
  geom_violin(color = "black",draw_quantiles = 0.5) +
  facet_wrap(vars(CASE_CTRL),ncol = 10) +
  xlab("Estradiol (uM)") +
  ylab("Intesity (a.u.)") +
  theme_bw() +
  stat_compare_means(ref.group = "0",label = "p.signif")
  #scale_fill_manual(values = c("green3","red3")) +
  #scale_color_manual(values = c("green4","red4")) +
```
## Plot distributions and save results for gated data

##Estradiol and Coppar plots
Green fluorescence 
```{r}
tbl_tidy %>% 
  filter(SCALE == "log") %>% 
  filter(NUM.IND %in% c("2")) %>% 
  filter(CHANNEL %in% c("GRN.B.HLog")) %>% 
  ggplot(aes(x = DOSE,y = INTENSITY,group = DOSE, fill = STRAIN)) +
  geom_violin(color = "black",draw_quantiles = 0.5) +
  facet_wrap(vars(CASE_CTRL),ncol = 10) +
  xlab("Estradiol and coppar (uM)") +
  ylab("Intesity (a.u.)") +
  theme_bw() +
  stat_compare_means(ref.group = "0",label = "p.signif")

```

Red fluorescence 
Got mmessy after making yeast with plamisds control!!!!
```{r}
tbl_tidy %>% 
  filter(SCALE == "log") %>% 
  filter(NUM.IND %in% c("2")) %>% 
  filter(CHANNEL %in% c("RED.R.HLog")) %>% 
  mutate(STRAIN = factor(STRAIN,levels = c("CENPK","Cup.Est","Estradiol","CUP"),ordered = TRUE)) %>%
  ggplot(aes(x = DOSE,y = INTENSITY,group = DOSE, fill = STRAIN)) +
  geom_violin(color = "black",draw_quantiles = 0.5) +
  facet_wrap(vars(STRAIN),ncol = 10) +
  xlab("Estradiol and coppar (uM)") +
  ylab("Intesity (a.u.)") +
  theme_bw() 
  #stat_compare_means(ref.group = "0",label = "p.signif")
```

```{r}
tbl_red_green %>% 
  filter(SCALE == "log") %>% 
  filter(STRAIN == "Cup.Est") %>% 
  ggplot(aes(GRN.B.HLog, RED.R.HLog)) +
  #geom_point() +
  geom_smooth(method = "loess") +
  facet_wrap(vars(DOSE),ncol = 10) +
  xlab("GRN.B.HLog Intensity (a.u.)") +
  ylab("RED.R.HLog Intesity (a.u.)") +
  theme_bw()


```

```{r}
tbl_red_green %>% 
   filter(SCALE == "log") %>% 
  filter(STRAIN == "Cup.Est") %>% 
  ggplot(aes(GRN.B.HLog, RED.R.HLog)) +
  geom_jitter() +
  facet_wrap(vars(DOSE),ncol = 10) +
  xlab("GRN.B.HLog Intensity (a.u.)") +
  ylab("RED.R.HLog Intesity (a.u.)") +
  theme_bw()
```



General RFP expression and density
```{r}
p_density_all_type_RFP =
 tbl_red_green %>% 
  ggplot(aes(RED.R.HLog, color = STRAIN, fill = REPLICATE)) +
  geom_density(alpha = 0.1, adjust = 0.0001) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(aspect.ratio = 1)

p_density_all_type_RFP
```


GFP expression depending of Estradiol conc.
```{r}
p_density_all_GPF_Est =
  tbl_red_green %>% 
  filter(STRAIN == c("Estradiol")) %>% 
  ggplot(aes(GRN.B.HLog, color = DOSE_1, fill = DOSE_1)) +
  geom_density(alpha = 0.1, adjust = 0.0001) +
  facet_wrap(vars(DOSE_1, INDUCER_1),nrow = 2) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("sfGFP (a.u., log-scale)") +
  theme(aspect.ratio = 1)

p_density_all_GPF_Est

```

GFP expression on Estradiol one plot
```{r}
p_density_all_GFP =
 tbl_red_green %>% 
  filter(STRAIN == c("Estradiol")) %>% 
  ggplot(aes(GRN.B.HLog, color = DOSE_1, fill = DOSE_1)) +
  geom_density(alpha = 0.1, adjust = 0.0001) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("sfGFP (a.u., log-scale)") +
  theme(aspect.ratio = 1)

p_density_all_GFP

```

GFP expression in control
```{r}
p_density_all_GFP_Control =
 tbl_red_green %>% 
  filter(STRAIN == c("CENPK")) %>% 
  filter(INDUCER_1 == c("Estradiol", "None")) %>% 
  ggplot(aes(GRN.B.HLog, color = DOSE_1, fill = DOSE_1)) +
  geom_density(alpha = 0.1, adjust = 0.0001) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("sfGFP (a.u., log-scale)") +
  theme(aspect.ratio = 1)

p_density_all_GFP_Control
```

Violin plot, not as nice as the one above!
```{r}
p_violin_all_GPF =
  tbl_red_green %>% 
  filter( INDUCER_1 == c("Estradiol","None")) %>% 
  ggplot(aes(x = DOSE_1, y = GRN.B.HLog, color = DOSE_1, fill = DOSE_1)) +
  geom_violin(alpha = 0.1, adjust = 0.0001) +
  facet_wrap(vars(CASE_CTRL),ncol = 10) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("Estradiol (uM)") +
  ylab("Intesity (a.u.)") +
  theme(aspect.ratio = 1)

p_violin_all_GPF

```


RFP expression depending of CUP conc.
```{r}
p_density_all_RFP_Cup =
  tbl_red_green %>% 
  filter(STRAIN == c("CUP")) %>% 
  ggplot(aes(RED.R.HLog, color = DOSE_1, fill = DOSE_1)) +
  geom_density(alpha = 0.1, adjust = 0.0001) +
  facet_wrap(vars(DOSE_1, INDUCER_1),nrow = 3) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(aspect.ratio = 1)

p_density_all_RFP_Cup
```

RFP expression depending of CUP conc.One plot
```{r}
p_density_all_GFP =
 tbl_red_green %>% 
  filter(STRAIN == c("CUP")) %>% 
  ggplot(aes(RED.R.HLog, color = DOSE_1, fill = DOSE_1)) +
  geom_density(alpha = 0.1, adjust = 0.0001) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(aspect.ratio = 1)

p_density_all_GFP
```

 expresstion in control
```{r}
p_density_all_RFP_Control =
 tbl_red_green %>% 
  filter(STRAIN == c("CENPK")) %>% 
  filter(INDUCER_1 == c("Cup","None")) %>% 
  ggplot(aes(GRN.B.HLog, color = DOSE_1, fill = DOSE_1)) +
  geom_density(alpha = 0.1, adjust = 0.0001) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(aspect.ratio = 1)

p_density_all_RFP_Control
```

Violin plot RFP, not as nice as the one above!
```{r}

p_violin_all_RPF =
  tbl_red_green %>% 
  filter( INDUCER_1 == c("Cup","None")) %>% 
  mutate(DOSE_1 = factor(DOSE_1,levels = c("0","100","500","1000"),ordered = TRUE)) %>%
  ggplot(aes(x = DOSE_1, y = RED.R.HLog, color = DOSE_1, fill = DOSE_1)) +
  geom_violin(alpha = 0.1, adjust = 0.0001) +
  facet_wrap(vars(CASE_CTRL),ncol = 10) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("Cupper (uM)") +
  ylab("Intesity (a.u.)") +
  theme(aspect.ratio = 1)

p_violin_all_RPF

```


All plots
```{r}

p_density_all_type_RFP
p_density_all_GPF_Est
p_density_all_GFP
p_density_all_GFP_Control
p_violin_all_GPF
p_density_all_RFP_Cup
p_density_all_GFP
p_density_all_RFP_Control
p_violin_all_RPF
```


