---
title: "R Notebook"
author: "Andrea Clausen Lind"
date: "23/03/2021"
output: html_notebook
---


## Load libraries
```{r, echo=FALSE}
library(flowCore)
library(tidyverse)
library(viridis)
library(hrbrthemes)
library(hexbin)
```

## Set working directory 
```{r,warning=FALSE}
setwd("/Users/lindandr/OneDrive - Chalmers University of Technology/PhD/Projects/Pathogen biosensor/Results/FACS/2021-07-28_RFP evaluation")
```

## Load data
```{r,warning=FALSE}
fs <- read.flowSet(path = "./Sample Group - 1/")
summary(fs)

csv_gateA <- list.files("./Sample Group - 1 - Gate A/", full.names = T)  %>% 
  lapply(., read.delim, sep = ",")

summary(csv_gateA)

```

## Format meta data
```{r}
meta_data = 
  tibble(file_id = names(fs@frames)) %>% 
  mutate(sample_id = gsub(".fcs","",file_id)) %>% 
  mutate(strain = gsub("_Data Source - 1","",sample_id))

#%>% 
  #separate(col = sample_id, into = c("strain","replicate","mat_pep_conc"), sep = "_",remove = F) %>% 
  #mutate(mat_pep_conc = ifelse(grepl("nM",mat_pep_conc),gsub("nM","",mat_pep_conc),"1000"))

head(meta_data) 

meta_data_A = 
  tibble(file_id = list.files("./Sample Group - 1 - Gate A/")) %>% 
  mutate(sample_id = gsub(".csv","",file_id)) %>% 
  mutate(strain = gsub("_Data Source - 1","",sample_id)) 

#%>% 
  #separate(col = sample_id, into = c("strain","replicate","mat_pep_conc"), sep = "_",remove = F) %>% 
  #mutate(mat_pep_conc = ifelse(grepl("nM",mat_pep_conc),gsub("nM","",mat_pep_conc),"1000"))

head(meta_data_A) 

```

## Let's extract the fs data as a tidy tibble
```{r}
# extract data from fs object
list = as.list(fs@frames)

# initialize empty data frame
df_flow = data.frame()

# Get no. of files
no_files = length(list)

# loop through all files and add each file data to empty data frame
for (i in 1:no_files) {
  
  # Extract file name
  file_name = names(list)[i]
  
  # Convert data to tibble and add file name
  file_data =
    list[[i]]@exprs %>% 
    as_tibble() %>% 
    mutate(FILE_NAME = file_name)
  
  # Join with empty data frame
  df_flow = rbind(df_flow,file_data)
}
```


## Convert the csv data into a tidy tibble
```{r}
# initialize empty data frame
df_flow_A = data.frame()

# Get no. of files
no_files = length(csv_gateA)

# loop through all files and add each file data to empty data frame
for (i in 1:no_files) {
  
  # Extract file name
  file_name = meta_data_A$sample_id[i]
  
  # Convert data to tibble and add file name
  file_data =
    csv_gateA[[i]] %>% 
    as_tibble() %>% 
    mutate(FILE_NAME = file_name)
  
  # Join with empty data frame
  df_flow_A = rbind(df_flow_A,file_data)
}

head(df_flow_A)
head(meta_data_A)
```


## Join with metadata
```{r}
df_full = 
  df_flow %>% 
  full_join(meta_data,by = c("FILE_NAME" = "file_id")) %>% 
  select(-FILE_NAME) %>% 
  rename("eGFP" = "FL2-A", "miRFP670" = "FL4-A") 

head(df_full)

df_full_A = 
  df_flow_A %>% 
  full_join(meta_data_A,by = c("FILE_NAME" = "sample_id")) %>% 
  select(-file_id, -Index) %>% 
  rename("FSC-A" = "FSC.A", "sample_id" = "FILE_NAME", "eGFP" = "EGFP.A.Compensated",) 

head(df_full_A)
```

## Filter out cells with negative intensity and log transform
```{r}
df_full = 
  df_full %>% 
  filter(eGFP > 0) %>% 
  mutate(log_eGFP = log10(eGFP+1)) %>%
  filter(miRFP670 > 0) %>% 
  mutate(log_miRFP670 = log10(miRFP670+1)) %>% 
  filter(`FSC-A` > 0) %>% 
  mutate(`log_FSC-A` = log10(`FSC-A`+1)) %>%
  mutate(strain = factor(strain,levels = c("APS2","RFP","ASC1 XII-1T1-RFP-C1","APS2 XI-2T1-RFP"), ordered = T))

head(df_full)

df_full_A = 
  df_full_A %>% 
  filter(eGFP > 0) %>% 
  mutate(log_eGFP = log10(eGFP+1)) %>%
  filter(miRFP670 > 0) %>% 
  mutate(log_miRFP670 = log10(miRFP670+1)) %>% 
  filter(`FSC-A` > 0) %>% 
  mutate(`log_FSC-A` = log10(`FSC-A`+1)) %>%
  mutate(strain = factor(strain,levels = c("APS2_A","RFP_A","ASC1 XII-1T1-RFP-C1_A","APS2 XI-2T1-RFP_A"), ordered = T)) 

head(df_full_A)

```


## Plot distributions and save results for non-gated data
```{r}

p_density_all =
  df_full %>% 
  #filter(strain == c("APS2","RFP","ASC1 XII-1T1-RFP-C1")) %>% 
  mutate(strain = factor(strain,levels = c("APS2","RFP","ASC1 XII-1T1-RFP-C1"), ordered = T)) %>% 
  ggplot(aes(log_miRFP670, color = strain, fill = strain)) +
  geom_density(alpha = 0.1, adjust = 0.0001) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(aspect.ratio = 1)

p_density2d_ASC2 =
  df_full %>% 
  filter(strain == c("ASC1 XII-1T1-RFP-C1")) %>% 
  ggplot(aes(x=log_miRFP670, y=`FSC-A`)) +
  geom_hex(bins = 100) +
  scale_fill_viridis(discrete = F,direction = -1, option = "A",begin = 0, end=0.9) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(legend.position = "none", 
        aspect.ratio = 1) 

p_density2d_ASC2_APS2 =
  df_full %>% 
  filter(strain == c("APS2", "ASC1 XII-1T1-RFP-C1")) %>% 
  ggplot(aes(x=log_miRFP670, y=`FSC-A`)) +
  geom_hex(bins = 100) +
  facet_wrap(vars(strain),nrow = 2) +
  scale_fill_viridis(discrete = F,direction = -1, option = "A",begin = 0, end=0.9) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(legend.position = "none", 
        aspect.ratio = 0.5) 

p_density2d_all =
  df_full %>%
  filter(strain == c("APS2","RFP","ASC1 XII-1T1-RFP-C1")) %>% 
  ggplot(aes(x = log_miRFP670, y = `FSC-A`)) +
  geom_hex(bins = 100) +
  facet_wrap(vars(strain),nrow = 3) +
  scale_fill_viridis(discrete = F,direction = -1, option = "A",begin = 0, end=0.9) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  ylab("FSC-A") +
  xlim(0,5) +
  theme(aspect.ratio = 0.3)

p_density_all_ridge =
  df_full %>% 
  #filter(strain == c("APS2","RFP","ASC1 XII-1T1-RFP-C1")) %>% 
  mutate(strain = factor(strain,levels = c("APS2","RFP","ASC1 XII-1T1-RFP-C1"), ordered = T)) %>% 
  filter(strain == c("APS2","RFP","ASC1 XII-1T1-RFP-C1")) %>%
  ggplot(aes(x = log_miRFP670, y = strain, color = strain, fill = strain)) +
  geom_density_ridges(alpha = 0.1, stat = "binline", binwidth = 0.01) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  theme_classic() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(legend.position = "none", aspect.ratio = 1)


p_density_all
p_density2d_ASC2
p_density2d_ASC2_APS2
p_density2d_all
p_density_all_ridge 

#ggsave(p_full, filename = "average_FACS.png",width = 6, height = 4)
#ggsave(p_partial, filename = "replicate_FACS.png",width = 6, height = 4)
#ggsave(p_density_all_ridge, filename = "ridge_RFP_ASC2.png",width = 6, height = 4)
```

## Plot distributions and save results for gated data
```{r}

p_density_all_A =
  df_full_A %>% 
  filter(strain == c("APS2_A","RFP_A","ASC1 XII-1T1-RFP-C1_A")) %>% 
  mutate(strain = factor(strain,levels = c("APS2_A","RFP_A","ASC1 XII-1T1-RFP-C1_A"), ordered = T)) %>%
  ggplot(aes(log_miRFP670, color = strain, fill = strain)) +
  geom_density(alpha = 0.1, adjust = 0.0001) +
  scale_color_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  scale_fill_viridis(discrete = T,direction = -1, option = "A",begin = 0.2, end=0.8) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(aspect.ratio = 1)

p_density2d_ASC2_A =
  df_full_A %>% 
  filter(strain == c("ASC1 XII-1T1-RFP-C1_A")) %>% 
  ggplot(aes(x=log_miRFP670, y=`FSC-A`)) +
  geom_hex(bins = 100) +
  scale_fill_viridis(discrete = F,direction = -1, option = "A",begin = 0, end=0.9) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(legend.position = "none", 
        aspect.ratio = 1) 

p_density2d_ASC2_APS2_A =
  df_full_A %>% 
  filter(strain == c("APS2_A", "ASC1 XII-1T1-RFP-C1_A")) %>% 
  ggplot(aes(x=log_miRFP670, y=`FSC-A`)) +
  geom_hex(bins = 100) +
  facet_wrap(vars(strain),nrow = 2) +
  scale_fill_viridis(discrete = F,direction = -1, option = "A",begin = 0, end=0.9) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  theme(legend.position = "none", 
        aspect.ratio = 0.5) 

p_density2d_all_A =
  df_full_A %>%
  filter(strain == c("APS2_A","RFP_A","ASC1 XII-1T1-RFP-C1_A")) %>% 
  ggplot(aes(x = log_miRFP670, y = `FSC-A`)) +
  geom_hex(bins = 100) +
  facet_wrap(vars(strain),nrow = 3) +
  scale_fill_viridis(discrete = F,direction = -1, option = "A",begin = 0, end=0.9) +
  theme_bw() +
  xlab("miRFP670 (a.u., log-scale)") +
  ylab("FSC-A") +
  xlim(0,5) +
  theme(aspect.ratio = 0.3)


p_density_all_A
p_density2d_ASC2_A
p_density2d_ASC2_APS2_A
p_density2d_all_A

#c("APS2_A","RFP_A","ASC1 XII-1T1-RFP-C1_A","APS2 XI-2T1-RFP_A")

#ggsave(p_density_all_A, filename = "histogram_FACS_gated_all.png",width = 6, height = 4)
ggsave(p_density_all_A, filename = "histogram_FACS_gated.png",width = 6, height = 4)

#ggsave(p_density2d_all_A, filename = "2Ddensity_FACS_gated.png",width = 6, height = 4)
```

```{r}
df_full %>% 
  mutate(test_log = log10(eGFP)) %>% 
  filter(is.nan(test_log))
```
## Find specific color IDs from viridis package
```{r}
library(scales)
show_col(viridis_pal(option = "A")(40))
````

